---
title: "7_5_7_6_basketball"
format: html
---

```{r}
library(tidyverse)
library(purrr)
```

# Load data

```{r}
df = read_csv("NBA Heights.csv")
power_forwards = df |> drop_na() |> pull("Power Forwards")
shooting_guards = df |> pull("Shooting Guards")
```

# Graph Power Forward Heights

Mean:

```{r}
mean(power_forwards)
```

Standard deviation:

```{r}
sd(power_forwards)
```

Histogram:

```{r}
ggplot(NULL, aes(x = power_forwards)) +
  geom_histogram(binwidth = 0.5)
```

# Take a random sample of 5 power forwards

```{r}
sample_of_5 = sample(power_forwards, 5)
sample_of_5
mean(sample_of_5)
```

# Graph 100 sample means

```{r}
sample_5_forwards = function(i) {
  # Copy your code from "Take a random sample of 5 power forwards" here
  
  
}
sample_mean_heights = map_dbl(1:100, sample_5_forwards)
ggplot(NULL, aes(x = sample_mean_heights)) +
  geom_histogram(binwidth = 0.1)
```

Mean of sample means:

```{r}
mean(sample_mean_heights)
```

Standard deviation of sample means:

```{r}
sd(sample_mean_heights)
```



# Graph Shooting Guard Heights

Mean:

```{r}
mean(shooting_guards)
```

Standard deviation:

```{r}
# copy and modify code from "Graph Power Forward Heights" section
```


Histogram:

```{r}
# copy and modify code from "Graph Power Forward Heights" section
```


# Take a random sample of 2 shooting guards

```{r}
# copy and modify code from "Take a random sample of 5 power forwards" section
```

# Take a random sample of 10 shooting guards

```{r}
# copy and modify code from "Take a random sample of 5 power forwards" section
```

# Graph the distributions of sample means (for samples of n=2)

```{r}
# copy and modify code from Graph 100 sample means where each sample has 2 shooting guards
```

# Graph the distributions of sample means (for samples of n=10)

```{r}
# copy and modify code from Graph 100 sample means where each sample has 10 shooting guards
```

